---
title: "step3"
author: "Tiam Heydari"
output: github_document
---

###Libraries
```{r}
library(pheatmap)
library(reshape2)
library(tidyverse)
library(GEOquery)
library(RColorBrewer)
library(cluster)
library(pvclust)
library(xtable)
library(limma)
library(dplyr)
library(lattice)
library(RCurl)
library(GEOquery)
library(knitr)
library(pheatmap)#
library(reshape2)#
library(purrr)
library(Hmisc)
library(psych)
library(MASS)
library(DAAG)
library(olsrr)
library(corrplot) # We'll use corrplot later on in this example too.
#library(rgl)#3D plot not working yet
#library(scatterplot3d)#3D plot not working yet
#library(visreg)
library(glmnet)
 library(lars)
set.seed(123)
```

#put all functions here:
```{r}
#-----------------------------------------------------------------
                #plot the correlation between probes, genes ect
                plot_correlation <- function(designated.dataframe.for.specific.gene,number.of.picked.probes){
                plot(designated.dataframe.for.specific.gene[,1:min(number.of.picked.probes,5)], pch=1,main=gene.name)
                #linear.model <-lm(expression~.,data=designated.dataframe.for.specific.gene)
                #summary( linear.model)
                datacor = cor(designated.dataframe.for.specific.gene[1:number.of.picked.probes])
                corrplot(datacor, method = "color",addCoef.col="grey",number.cex= 7/ncol(designated.dataframe.for.specific.gene))
                #quick visualizing data
                auto.sel <- designated.dataframe.for.specific.gene[,1:number.of.picked.probes]
                #plot : distribution , linear , and correlation:
                pairs.panels(auto.sel, col="red")
                }
#-----------------------------------------------------------------
#-----------------------------------------------------------------
#-----------------------------------------------------------------
#-----------------------------------------------------------------
#-----------------------------------------------------------------
#-----------------------------------------------------------------
#-----------------------------------------------------------------
```



##1- Here we load the data from a local directoty. 
```{r}
rawdata<- readRDS("~/Desktop/BIOF/Group project/Step3-multiple regression/cor_test_results_PCA_lapply_V4.rds")

load("~/Desktop/BIOF/Group project/Step3-multiple regression/rosmap_postprocV2.RData")

probes_subjects<- as.data.frame( readRDS("~/Desktop/BIOF/Group project/Step3-multiple regression/probes_subjects_PCA_adjusted_V4.RDS"))

subjects_genes<- as.data.frame(  readRDS("~/Desktop/BIOF/Group project/Step3-multiple regression/subjects_genes_PCA_adjusted_V4.RDS"))

```


```{r}
head(rawdata)
head(subjects_genes)
head(probes_subjects)
hist(rawdata$pvalue)

```



#1.Selecting only genes that has a probe with P value greater than the P.val.tresh:
```{r}
P.val.tresh <- 0.05
max.number.of.probes <- 20
number.of.genes <- ncol(subjects_genes)
significance.of.gene.probes <- lapply(1:number.of.genes, function(i){
                gene.number <- i # then we can put the whole thing in a function
                gene.name  <- names(subjects_genes)[gene.number]
                # exclude of subse of raw data which is for this gene
                rawdata.for.specific.gene <-rawdata %>% filter(gene==gene.name)
                # sort the raws (which are prob numbers) due to P value:
                rawdata.for.specific.gene <-          
                rawdata.for.specific.gene[order(rawdata.for.specific.gene$adjusted.pvalue),]
                #gene.expressions<-data.frame(expression=subjects_genes[,gene.name])
                #names.of.ordered.probes<-rawdata.for.specific.gene$probe
                #ordered.probe.value<-as.data.frame(t(probes_subjects[as.character(names.of.ordered.probes),]))
                #designated.dataframe.for.specific.gene<-cbind(gene.expressions,ordered.probe.value)
                #head(rawdata.for.specific.gene,30)
                #head(designated.dataframe.for.specific.gene)
                if(rawdata.for.specific.gene[1,"adjusted.pvalue"] < P.val.tresh){
                     number.of.sig.probes <- 0
                     for(j in 1:max.number.of.probes) 
                       {
                         if(rawdata.for.specific.gene[j,"adjusted.pvalue"] <P.val.tresh)
                          {
                           number.of.sig.probes <- (number.of.sig.probes+1)
                         }
                       else{ break }
                     }
                     
                   return(c(gene.number,number.of.sig.probes))
                }
                else{ return(c(0,0))}
                
})
significance.of.gene.probes<-as.data.frame(t(as.data.frame(significance.of.gene.probes)))
#row.id.sig.genes<-as.matrix(row.id.sig.genes)
names(significance.of.gene.probes) <- c("gene_number", "number_probes")
#row.id.sig.genes<-filter(significance.of.gene.probes,gene_number!=0)
significance.of.gene.probes<-filter(significance.of.gene.probes,gene_number!=0)
significance.of.gene.probes
```

```{r}
significance.of.gene.probes_raw<- significance.of.gene.probes
significance.of.gene.probes

hist(significance.of.gene.probes$number_probes,20, main = "distribution of probes with p value lower than 0.05")

pdf("~/Desktop/BIOF/Group project/Step3-multiple regression/results/plot/histogram.number.of.probes.pdf")
hist(significance.of.gene.probes$number_probes,20, main = "distribution of probes with p value lower than 0.05")
dev.off()

```


now we found the row number of genes that at least had a one fignificant probe with the p value less than the treshold and the number of fignificant probes that each gene has. 
Before that note that to access the genes:
significance.of.gene.probes$gene_number
is used

before that here we filter only genes that have more than 1 significant probe:
```{r}
significance.of.gene.probes<-filter(significance.of.gene.probes,number_probes > 1)
hist(significance.of.gene.probes$number_probes,100)
nrow(significance.of.gene.probes)
row.names(significance.of.gene.probes) <-as.character((names(subjects_genes)[(significance.of.gene.probes[,1])]))
significance.of.gene.probes

```



______________________________________________________________________________________________________
#2 fit models to a single gene
##2.1 extract matrixes for each gene :

##2.2 fit  linear models to each significant gene
```{r}

                k <-1 # k could be between [ 1,nrow(significance.of.gene.probes) ]
                gene.number <-significance.of.gene.probes[k,1]
                gene.name  <- names(subjects_genes)[gene.number]
                number.of.picked.probes <- significance.of.gene.probes[k,2]
               number.of.picked.probes
                 # exclude of subse of raw data which is for this gene
                rawdata.for.specific.gene <-rawdata %>% filter(gene==gene.name)
                
                # sort the raws (which are prob numbers) due to P value:
                rawdata.for.specific.gene <-          
                rawdata.for.specific.gene[order(rawdata.for.specific.gene$adjusted.pvalue),]
                gene.expressions<-data.frame(expression=subjects_genes[,gene.name])
                names.of.ordered.probes<-rawdata.for.specific.gene$probe
                ordered.probe.value<-as.data.frame(t(probes_subjects[as.character(names.of.ordered.probes),]))
                designated.dataframe.for.specific.gene<-cbind(gene.expressions,ordered.probe.value)
                rawdata.for.specific.gene<-rawdata.for.specific.gene[1:number.of.picked.probes,]
                designated.dataframe.for.specific.gene<- designated.dataframe.for.specific.gene[,1:(number.of.picked.probes+1)]
                head(rawdata.for.specific.gene)
                head(designated.dataframe.for.specific.gene)
          

                #k
                #head(rawdata.for.specific.gene)
                #head(designated.dataframe.for.specific.gene)

                  number.of.picked.probes <- significance.of.gene.probes[k,2]
                #change the name of the dataframe colums from V1 to Vn  to make fitting easy:
                make.no.names <- as.data.frame( matrix(nrow = 1,ncol =number.of.picked.probes ) )
                designated.dataframe.for.specific.gene_NOname <- designated.dataframe.for.specific.gene
                names(designated.dataframe.for.specific.gene_NOname) <- c("expression",names(make.no.names))
                
               train.designated.dataframe.for.specific.gene_NOname <-designated.dataframe.for.specific.gene_NOname[1:385,]
               test.designated.dataframe.for.specific.gene_NOname <-designated.dataframe.for.specific.gene_NOname[386:481,]

               
               
                #_______________stepwise/forward/backwar_______________________
                fit.full <- lm(expression~.,data=train.designated.dataframe.for.specific.gene_NOname)
                fit_single <- lm(expression~V1,data=train.designated.dataframe.for.specific.gene_NOname)
                step_forward <- stepAIC(fit_single, direction="forward",trace = F)
                step_backward <- stepAIC(fit.full, direction="backward",trace = F)
                #step_backward$anova # display results
                #step_forward$anova # display results
                fit_forward<- lm(step_forward)
                fit_backward<- lm(step_backward)

                #_______________stepwise/forward/backwar_______________________
                
                #_______________LASSO_______________________
                #https://www.youtube.com/watch?v=fAPCaue8UKQ
                matrix_of_predictors_train <- as.matrix(train.designated.dataframe.for.specific.gene_NOname[,-1])
                 matrix_of_predictors_test <- as.matrix(test.designated.dataframe.for.specific.gene_NOname[,-1])
                response <- as.matrix(train.designated.dataframe.for.specific.gene_NOname[,1])
                lasso.fit <- glmnet(matrix_of_predictors_train,response)
                lasso.cv <- cv.glmnet(matrix_of_predictors_train,response,n=3)
                msp_cv_fit_lasso <- lasso.cv$cvm[lasso.cv$lambda == lasso.cv$lambda.min]
                #_______________LASSO_______________________
                
                
                #--------------find the number of probes in each model-------
                n_probes_single<-(dim(as.matrix(fit_single$coefficients))[1]-1)
                n_probes_full<-(dim(as.matrix(fit.full$coefficients))[1]-1)
                n_probes_forward<-(dim(as.matrix(fit_forward$coefficients))[1]-1)
                n_probes_backward<-(dim(as.matrix(fit_backward$coefficients))[1]-1)
                
                #for lasso 
                temp.coefficient<-as.data.frame(as.matrix(   coef(lasso.cv, s = "lambda.min")) ) 
                names(temp.coefficient) <- "coef"
                n_probes_lasso<-nrow(filter(temp.coefficient,coef!=0))
                #--------------find the number of probes in each model-------
                
                
                
                #------------------ MSP on train data -----------------------------------
                #from:  https://stackoverflow.com/questions/39811656/r-calculate-test-mse-given-a-trained-model-from-a-training-set-and-a-test-set
                msp_train_fit_single<-mean((train.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_single, train.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                msp_train_fit_full<-mean((train.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit.full, train.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                msp_train_fit_forward<-mean((train.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_forward, train.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                msp_train_fit_backward<-mean((train.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_backward, train.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                msp_train_fit_lasso<-mean((train.designated.dataframe.for.specific.gene_NOname$expression -predict.glmnet(lasso.fit,matrix_of_predictors_train)) ^ 2)
                #------------------ MSP on train data -----------------------------------  
                
                                
                
                #------------------ MSP on test data -----------------------------------
                #from:  https://stackoverflow.com/questions/39811656/r-calculate-test-mse-given-a-trained-model-from-a-training-set-and-a-test-set
                
                msp_test_fit_single<-mean((test.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_single, test.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                msp_test_fit_full<-mean((test.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit.full, test.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                msp_test_fit_forward<-mean((test.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_forward, test.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                msp_test_fit_backward<-mean((test.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_backward, test.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                msp_test_fit_lasso<-mean((test.designated.dataframe.for.specific.gene_NOname$expression -predict.glmnet(lasso.fit,matrix_of_predictors_test)) ^ 2)
                #------------------ MSP on test data -----------------------------------                
                
                #cross validating the resutls_______________________
                cv_fit_single<-cv.lm(train.designated.dataframe.for.specific.gene_NOname,fit_single, m=3,seed = 2018,printit = F,plotit =  F)
                msp_cv_fit_single <-attr(cv_fit_single, "ms")
                
                cv_fit_full<-cv.lm(train.designated.dataframe.for.specific.gene_NOname,fit.full, m=3,seed = 2018,printit = F,plotit =  F)
                msp_cv_fit_full <-attr(cv_fit_full, "ms")
                
                cv_fit_forward<-cv.lm(train.designated.dataframe.for.specific.gene_NOname,fit_forward, m=3,seed = 2018,printit = F,plotit =  F)
                msp_cv_fit_forward <-attr(cv_fit_forward, "ms")
                
                cv_fit_backward<-cv.lm(train.designated.dataframe.for.specific.gene_NOname,fit_backward, m=3,seed = 2018,printit = F,plotit =  F)
                msp_cv_fit_backward<-attr(cv_fit_backward, "ms")
                 #cross validating the resutls_______________________
                
                
                                    
                       #------------------ abs on test data -----------------------------------
                #from:  https://stackoverflow.com/questions/39811656/r-calculate-test-mse-given-a-trained-model-from-a-training-set-and-a-test-set
                
                abs_test_fit_single<-mean(abs(test.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_single, test.designated.dataframe.for.specific.gene_NOname))/test.designated.dataframe.for.specific.gene_NOname$expression)
                abs_test_fit_full<-mean(abs(test.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit.full, test.designated.dataframe.for.specific.gene_NOname))/test.designated.dataframe.for.specific.gene_NOname$expression)
                abs_test_fit_forward<-mean(abs(test.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_forward, test.designated.dataframe.for.specific.gene_NOname))/test.designated.dataframe.for.specific.gene_NOname$expression)
                abs_test_fit_backward<-mean(abs(test.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_backward, test.designated.dataframe.for.specific.gene_NOname))/test.designated.dataframe.for.specific.gene_NOname$expression)
                abs_test_fit_lasso<-mean(abs(test.designated.dataframe.for.specific.gene_NOname$expression -predict.glmnet(lasso.fit,matrix_of_predictors_test))/test.designated.dataframe.for.specific.gene_NOname$expression)
                #------------------ abs on test data -----------------------------------      
                


```

##non linear models:
```{r}
                   #----------------higher degree fitting--------------------------------
                   higher_deg <- lapply(1:20, function(i){
                    degree <- i
                    fit_x <- lm(expression~ poly(V1,degree) ,data=train.designated.dataframe.for.specific.gene_NOname)
                    msp_train_x<-mean((train.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_x, train.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                    msp_test_x<-mean((test.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_x, test.designated.dataframe.for.specific.gene_NOname)) ^ 2)                    
                    return(c(degree,msp_train_x,msp_test_x))
                  })
                  higher_deg<-as.data.frame(t(as.data.frame(higher_deg)))
                  names(higher_deg) <- c("degree","train","test")
                  higher_msp<-min(higher_deg$test)
                  degree<-which(higher_deg$test==higher_msp)
                  #----------------higher degree fitting--------------------------------                  
                  #plot
                  ggplot(higher_deg, aes(degree,test)) +
                      geom_line(aes(degree,test), colour="blue") + 
                      geom_line(aes(degree,train), colour = "grey") +
                        geom_point(aes(degree,test), colour="blue") + 
                      geom_point(aes(degree,train), colour = "grey") +
                      ylab("erroe") + 
                      xlab("degree")+
                      theme(axis.line = element_line(colour = "black"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_blank()) 
#ggplot(train.designated.dataframe.for.specific.gene_NOname, aes(expression,V1)) + geom_point() + stat_smooth(method = "lm")+
#stat_smooth(method = "lm", formula = y~ poly(x,degree), size = 1,col = "red")
                  
```



##outputs:
```{r}
                
                n_probes_single
                msp_train_fit_single
                msp_cv_fit_single
                msp_test_fit_single
                
                n_probes_full
                msp_train_fit_full
                msp_cv_fit_full
                msp_test_fit_full
                
                n_probes_forward
                msp_train_fit_forward
                msp_cv_fit_forward
                msp_test_fit_forward
                
                n_probes_backward
                msp_train_fit_backward
                msp_cv_fit_backward
                msp_test_fit_backward
                
                n_probes_lasso
                msp_train_fit_lasso
                msp_cv_fit_lasso
                msp_test_fit_lasso

```


Plots:
```{r}
                #plot the correlation between probes, genes ect
                plot_correlation(designated.dataframe.for.specific.gene,number.of.picked.probes)
                plot(lasso.fit)
                plot(lasso.cv)
                
```




______________________________________________________________________________________________________
#3 fit linear models to all genes:

```{r}
 MS.of.fitts.for.all.sig.genes   <- lapply(1:nrow(significance.of.gene.probes), function(i){
# MS.of.fitts.for.all.sig.genes   <- lapply(1:5, function(i){
                k <-i # k could be between [ 1,nrow(significance.of.gene.probes) ]
                gene.number <-significance.of.gene.probes[k,1]
                gene.name  <- names(subjects_genes)[gene.number]
                number.of.picked.probes <- significance.of.gene.probes[k,2]
                #number.of.picked.probes
                 # exclude of subse of raw data which is for this gene
                rawdata.for.specific.gene <-rawdata %>% filter(gene==gene.name)
                
                # sort the raws (which are prob numbers) due to P value:
                rawdata.for.specific.gene <-          
                rawdata.for.specific.gene[order(rawdata.for.specific.gene$adjusted.pvalue),]
                gene.expressions<-data.frame(expression=subjects_genes[,gene.name])
                names.of.ordered.probes<-rawdata.for.specific.gene$probe
                ordered.probe.value<-as.data.frame(t(probes_subjects[as.character(names.of.ordered.probes),]))
                designated.dataframe.for.specific.gene<-cbind(gene.expressions,ordered.probe.value)
                rawdata.for.specific.gene<-rawdata.for.specific.gene[1:number.of.picked.probes,]
                designated.dataframe.for.specific.gene<- designated.dataframe.for.specific.gene[,1:(number.of.picked.probes+1)]
                #head(rawdata.for.specific.gene)
                #head(designated.dataframe.for.specific.gene)
                #k
                #head(rawdata.for.specific.gene)
                #head(designated.dataframe.for.specific.gene)
                #head(rawdata.for.specific.gene)
                #head(designated.dataframe.for.specific.gene)
                #change the name of the dataframe colums from V1 to Vn  to make fitting easy:
                make.no.names <- as.data.frame( matrix(nrow = 1,ncol =number.of.picked.probes ) )
                designated.dataframe.for.specific.gene_NOname <- designated.dataframe.for.specific.gene
                names(designated.dataframe.for.specific.gene_NOname) <- c("expression",names(make.no.names))
               train.designated.dataframe.for.specific.gene_NOname <-designated.dataframe.for.specific.gene_NOname[1:385,]
               test.designated.dataframe.for.specific.gene_NOname <-designated.dataframe.for.specific.gene_NOname[386:481,]

                #_______________stepwise/forward/backwar_______________________
                fit.full <- lm(expression~.,data=train.designated.dataframe.for.specific.gene_NOname)
                fit_single <- lm(expression~V1,data=train.designated.dataframe.for.specific.gene_NOname) 
               step_forward <- stepAIC(fit_single, direction="forward",trace = F)
                step_backward <- stepAIC(fit.full, direction="backward",trace = F)
                #step_backward$anova # display results
                #step_forward$anova # display results
                fit_forward<- lm(step_forward)
                fit_backward<- lm(step_backward)

                #_______________stepwise/forward/backwar_______________________
                
                #_______________LASSO_______________________
                #https://www.youtube.com/watch?v=fAPCaue8UKQ
                matrix_of_predictors_train <- as.matrix(train.designated.dataframe.for.specific.gene_NOname[,-1])
                 matrix_of_predictors_test <- as.matrix(test.designated.dataframe.for.specific.gene_NOname[,-1])
                response <- as.matrix(train.designated.dataframe.for.specific.gene_NOname[,1])
                lasso.fit <- glmnet(matrix_of_predictors_train,response)
                lasso.cv <- cv.glmnet(matrix_of_predictors_train,response,n=3)
                msp_cv_fit_lasso <- lasso.cv$cvm[lasso.cv$lambda == lasso.cv$lambda.min]
                #_______________LASSO_______________________
                
                
                #--------------find the number of probes in each model-------
                n_probes_single<-(dim(as.matrix(fit_single$coefficients))[1]-1)
                n_probes_full<-(dim(as.matrix(fit.full$coefficients))[1]-1)
                n_probes_forward<-(dim(as.matrix(fit_forward$coefficients))[1]-1)
                n_probes_backward<-(dim(as.matrix(fit_backward$coefficients))[1]-1)
                
                #for lasso 
                temp.coefficient<-as.data.frame(as.matrix(   coef(lasso.cv, s = "lambda.min")) ) 
                names(temp.coefficient) <- "coef"
                n_probes_lasso<-nrow(filter(temp.coefficient,coef!=0))
                #--------------find the number of probes in each model-------
                
                
                
                #------------------ MSP on train data -----------------------------------
                #from:  https://stackoverflow.com/questions/39811656/r-calculate-test-mse-given-a-trained-model-from-a-training-set-and-a-test-set
                msp_train_fit_single<-mean((train.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_single, train.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                msp_train_fit_full<-mean((train.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit.full, train.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                msp_train_fit_forward<-mean((train.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_forward, train.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                msp_train_fit_backward<-mean((train.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_backward, train.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                msp_train_fit_lasso<-mean((train.designated.dataframe.for.specific.gene_NOname$expression -predict.glmnet(lasso.fit,matrix_of_predictors_train)) ^ 2)
                #------------------ MSP on train data -----------------------------------  
                
                                
                
                #------------------ MSP on test data -----------------------------------
                #from:  https://stackoverflow.com/questions/39811656/r-calculate-test-mse-given-a-trained-model-from-a-training-set-and-a-test-set
                
                msp_test_fit_single<-mean((test.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_single, test.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                msp_test_fit_full<-mean((test.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit.full, test.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                msp_test_fit_forward<-mean((test.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_forward, test.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                msp_test_fit_backward<-mean((test.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_backward, test.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                msp_test_fit_lasso<-mean((test.designated.dataframe.for.specific.gene_NOname$expression -predict.glmnet(lasso.fit,matrix_of_predictors_test)) ^ 2)
                #------------------ MSP on test data -----------------------------------                
                
                #cross validating the resutls_______________________
                cv_fit_single<-cv.lm(train.designated.dataframe.for.specific.gene_NOname,fit_single, m=3,seed = 2018,printit = F,plotit =  F)
                msp_cv_fit_single <-attr(cv_fit_single, "ms")
                
                cv_fit_full<-cv.lm(train.designated.dataframe.for.specific.gene_NOname,fit.full, m=3,seed = 2018,printit = F,plotit =  F)
                msp_cv_fit_full <-attr(cv_fit_full, "ms")
                
                cv_fit_forward<-cv.lm(train.designated.dataframe.for.specific.gene_NOname,fit_forward, m=3,seed = 2018,printit = F,plotit =  F)
                msp_cv_fit_forward <-attr(cv_fit_forward, "ms")
                
                cv_fit_backward<-cv.lm(train.designated.dataframe.for.specific.gene_NOname,fit_backward, m=3,seed = 2018,printit = F,plotit =  F)
                msp_cv_fit_backward<-attr(cv_fit_backward, "ms")
                 #cross validating the resutls_______________________

                
                  #----------------higher degree fitting--------------------------------
                   higher_deg <- lapply(2:7, function(k){
                    degree <- k
                    fit_x <- lm(expression~ poly(V1,degree) ,data=train.designated.dataframe.for.specific.gene_NOname)
                    msp_train_x<-mean((train.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_x, train.designated.dataframe.for.specific.gene_NOname)) ^ 2)
                    msp_test_x<-mean((test.designated.dataframe.for.specific.gene_NOname$expression -predict.lm(fit_x, test.designated.dataframe.for.specific.gene_NOname)) ^ 2)                    
                    return(c(degree,msp_train_x,msp_test_x))
                  })
                  higher_deg<-as.data.frame(t(as.data.frame(higher_deg)))
                  names(higher_deg) <- c("degree","train","test")
                  higher_msp<-min(higher_deg$test)
                  degree<-(which(higher_deg$test==higher_msp)+1)
                  #----------------higher degree fitting--------------------------------   
                
                  #----------other outputs:----------------------------
                    highes_Pvalue <-rawdata.for.specific.gene$adjusted.pvalue[1]
                    best_model <- "single"
                    best_msp <-msp_test_fit_single
                    if(msp_test_fit_full<best_msp){best_model <- "full"
                                       best_msp <-msp_test_fit_full }
                    if(msp_test_fit_forward<best_msp){best_model <- "forward"
                                       best_msp <-msp_test_fit_forward }
                    if(msp_test_fit_backward<best_msp){best_model <- "backward"
                                       best_msp <-msp_test_fit_backward }
                    if(msp_test_fit_lasso<best_msp){best_model <- "lasso"
                                       best_msp <-msp_test_fit_lasso }
                    if(higher_msp<best_msp){best_model <- "higher"
                                       best_msp <-higher_msp }

                #----------other outputs:----------------------------
                  
                  
                
                return(as.data.frame(c(number.of.picked.probes,highes_Pvalue,best_model,best_msp,n_probes_single,msp_train_fit_single,msp_cv_fit_single,msp_test_fit_single,n_probes_full,msp_train_fit_full,msp_cv_fit_full, msp_test_fit_full,n_probes_forward, msp_train_fit_forward,msp_cv_fit_forward,msp_test_fit_forward,n_probes_backward,msp_train_fit_backward,msp_cv_fit_backward,msp_test_fit_backward,n_probes_lasso,msp_train_fit_lasso,msp_cv_fit_lasso,msp_test_fit_lasso,higher_msp,degree)))
                })
                

MS.of.fitts.for.all.sig.genes<-as.data.frame(t(as.data.frame(MS.of.fitts.for.all.sig.genes)))
names(MS.of.fitts.for.all.sig.genes) <- c("number_significant_probes","highes_Pvalue","best_model","best_msp","single_n","single_train","single_cv","single_test","full_n","full_train","full_cv","full_test", "forward_n","forward_train","forward_cv","forward_test", "backward_n","backward_train","backward_cv","backward_test","lasso_n", "lasso_train","lasso_cv","lasso_test","higher_msp","higher_degree")
row.names(MS.of.fitts.for.all.sig.genes) <-as.character((names(subjects_genes)[(significance.of.gene.probes[,1])]))
```








```{r}

```


```{r}
MS.of.fitts.for.all.sig.genes
saveRDS(MS.of.fitts.for.all.sig.genes,file = "~/Desktop/BIOF/Group project/Step3-multiple regression/results/data/MSP.rda")

```

This plot shows that in more than 50% of the genes, the full model predicts the gene expression. After that interestingly non-linear model of the single probe has the best performance, this suggest hight amount of non linearaty in the model. aslo lasso shows a good performance and the linear single probe shows the weakest predicts.
```{r}
barplot(prop.table(table(MS.of.fitts.for.all.sig.genes$best_model)))
barplot(prop.table(table(MS.of.fitts.for.all.sig.genes$higher_degree)))
pdf("~/Desktop/BIOF/Group project/Step3-multiple regression/results/plot/best.mode.pdf")
barplot(prop.table(table(MS.of.fitts.for.all.sig.genes$best_model)))
barplot(prop.table(table(MS.of.fitts.for.all.sig.genes$higher_degree)))
dev.off()
```






```{r}
x<-0
selected.metho <- "single"
selceted.method.data<-filter(MS.of.fitts.for.all.sig.genes, best_model==selected.metho)
x$full_train<- as.numeric(as.character(selceted.method.data$full_train))
x$full_test<- as.numeric(as.character(selceted.method.data$full_test))
y<-lapply(1:300, function(i){
  y<- x$full_train[i]/x$full_test[i]
})
h<-hist(as.numeric(y),main = selected.metho,xlab = "[test error]/[train error]")
myplot_<-0
mysum<- sum(h$counts)
myplot_<-cbind(as.data.frame(as.numeric(h$mids) ) ,as.data.frame(as.numeric(h$counts) )/mysum) 
names(myplot_)<- c("x","y")
myplot_single <-myplot_


selected.metho <- "backward"
selceted.method.data<-filter(MS.of.fitts.for.all.sig.genes, best_model==selected.metho)
x$full_train<- as.numeric(as.character(selceted.method.data$full_train))
x$full_test<- as.numeric(as.character(selceted.method.data$full_test))
y<-lapply(1:300, function(i){
  y<- x$full_train[i]/x$full_test[i]
})
h<-hist(as.numeric(y),main = selected.metho,xlab = "[test error]/[train error]")
myplot_<-0
mysum<- sum(h$counts)
myplot_<-cbind(as.data.frame(as.numeric(h$mids) ) ,as.data.frame(as.numeric(h$counts) )/mysum) 
names(myplot_)<- c("x","y")
myplot_backward<-myplot_



selected.metho <- "lasso"
selceted.method.data<-filter(MS.of.fitts.for.all.sig.genes, best_model==selected.metho)
x$full_train<- as.numeric(as.character(selceted.method.data$full_train))
x$full_test<- as.numeric(as.character(selceted.method.data$full_test))
y<-lapply(1:300, function(i){
  y<- x$full_train[i]/x$full_test[i]
})
h<-hist(as.numeric(y),main = selected.metho,xlab = "[test error]/[train error]")
myplot_<-0
mysum<- sum(h$counts)
myplot_<-cbind(as.data.frame(as.numeric(h$mids) ) ,as.data.frame(as.numeric(h$counts) )/mysum) 
names(myplot_)<- c("x","y")
myplot_lasso<-myplot_



selected.metho <- "full"
selceted.method.data<-filter(MS.of.fitts.for.all.sig.genes, best_model==selected.metho)
x$full_train<- as.numeric(as.character(selceted.method.data$full_train))
x$full_test<- as.numeric(as.character(selceted.method.data$full_test))
y<-lapply(1:300, function(i){
  y<- x$full_train[i]/x$full_test[i]
})
h<-hist(as.numeric(y),main = selected.metho,xlab = "[test error]/[train error]")
myplot_<-0
mysum<- sum(h$counts)
myplot_<-cbind(as.data.frame(as.numeric(h$mids) ) ,as.data.frame(as.numeric(h$counts) )/mysum) 
names(myplot_)<- c("x","y")
myplot_full<-myplot_



selected.metho <- "higher"
selceted.method.data<-filter(MS.of.fitts.for.all.sig.genes, best_model==selected.metho)
x$full_train<- as.numeric(as.character(selceted.method.data$full_train))
x$full_test<- as.numeric(as.character(selceted.method.data$full_test))
y<-lapply(1:300, function(i){
  y<- x$full_train[i]/x$full_test[i]
})
h<-hist(as.numeric(y),main = selected.metho,xlab = "[test error]/[train error]")
myplot_<-0
mysum<- sum(h$counts)
myplot_<-cbind(as.data.frame(as.numeric(h$mids) ) ,as.data.frame(as.numeric(h$counts) )/mysum) 
names(myplot_)<- c("x","y")
myplot_higher<-myplot_



ggplot()+

      geom_smooth(data=myplot_single, aes(x=x, y=y),se=FALSE, method="loess", span=1,colour="black")+
  

      geom_smooth(data=myplot_full, aes(x=x, y=y),se=FALSE, method="loess", span=1,colour="red")+
  
      geom_smooth(data=myplot_backward, aes(x=x, y=y),se=FALSE, method="loess", span=1,colour="blue")+
  

      geom_smooth(data=myplot_lasso, aes(x=x, y=y),se=FALSE, method="loess", span=1,colour="orange")+
  

      geom_smooth(data=myplot_higher, aes(x=x, y=y),se=FALSE, method="loess", span=1,colour="pink")+
      
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))

  
```

```{r}
```



```{r}

x$best<- as.numeric(as.character(selceted.method.data$best_msp))
x$single<- as.numeric(as.character(selceted.method.data$single_test))
y<-lapply(1:300, function(i){
  y<- x$best[i]/x$single[i]
})
selceted.method.data
hist(as.numeric(y),100)
```

______________________________________________________________________________________________________



______________________________________________________________________________________________________





Alternatively, you can perform all-subsets regression using the leaps( ) function from the leaps package. In the following code nbest indicates the number of subsets of each size to report. Here, the ten best models will be reported for each subset size (1 predictor, 2 predictors, etc.). 




