---
title: "Geneset Enrichment Analysis"
author: "Zohreh Sharafian"
date: "March 27, 2018"
output: github_document
---

We load related library packages to understand and verify the biological aspects of our analysis.We use "ermineR" package for gene enrichment analysis [ref].
```{r}
library(tidyverse)
library(reshape2)
library(devtools)
library(ermineR)
ermineR:::findJava()
```
### Loading data

WE load a data set from eQTM analysis that we have peroformed in Step 2, including all the adjusted P values for analysing single probes.
```{r}
 
original_data <- readRDS("C:/Users/zohre/Desktop/Repo_team_Gene_Heroes/Step4/cor_test_results_PCA_lapply_V4.rds")

head(original_data)

```
### Modifiying data
We remove the second part of gene names as "ermineR" accepts the HGNC symbol of the genes.

```{r}

modified_data <- original_data

modified_data$new_gene_name <- sub(':.*$',"",modified_data$gene)

modified_data <- modified_data[c("gene","new_gene_name", "probe","estimate", "pvalue", "adjusted.pvalue")]

head(modified_data)
```
### Preparing the inputs

We extract three columns including "new gane name", "probe", and "adjusted P value" for all the genes in our data set.Next, we count the number of probes that are assiociated with a particular gene and assign zero to those probes that do not coresspond to any gene in the data set.
```{r}

extracted_data <- modified_data[,c(2, 3,6)]

filtered_adjusted_pvalue <- extracted_data[extracted_data$adjusted.pvalue<0.05,]
#filtered_adjusted_pvalue= extracted_data
all_genes_names=unique(modified_data$new_gene_name);
remaining_names=setdiff(all_genes_names,filtered_adjusted_pvalue$new_gene_name)
remaining_names=as.data.frame(remaining_names);
remaining_names$count=0;

filtered_adjusted_pvalue [1:20,]

```
We realize that there are 536 gene that have one or more associated probe.
```{r}

nrow(filtered_adjusted_pvalue)

length(unique(filtered_adjusted_pvalue$new_gene_name))


```

We generate a new data set including the gene names and the count of related probes for each gene.We got the scores based on the number of probes corresponding to a particular gene.Those genes that have not any related probe get zero value.
```{r}
library(tidyverse)

gene_list <- filtered_adjusted_pvalue %>% count(new_gene_name)
gene_list[1:15,]
colnames(remaining_names)=c("new_gene_name","n")
gene_list=rbind(gene_list,remaining_names)
gene_list$n=exp(gene_list$n)
class(gene_list)

```
We provide what ermineJ requires as inputs including:
 
  1.The gene ontology (GO) XML file
  2.The annotation file
  The annotation file and GO XML files together provide the gene sets.
  3.The list of genes and corresponding scores to be analyzed.

```{r}

if (!file.exists("GO.xml")) { goToday("GO.xml") }

ermineInputGeneScores <- gene_list %>% 
  mutate(absolute_n = abs(n)) %>% 
  na.omit() %>% 
  as.data.frame() %>% 
  arrange(desc(absolute_n)) %>% 
  column_to_rownames("new_gene_name")

```

We use the Precision-Recall method to perform the enrichment analysis.
```{r}
enrichmentResult <- precRecall(scores = ermineInputGeneScores, 
                               scoreColumn = 1, 
                               bigIsBetter = TRUE, 
                               annotation = "Generic_human", 
                               aspects = "B", 
                               iterations = 10000, 
                               geneSetDescription = "GO.xml") 
```

The result show the "correctedMFPvalue"=1 for all the genes regardless of the number of corresponding probes.This result shows that there is not any relationship between the number of significant probes and the multifunctionality of the genes as there is no significant p value for the gene sets.
```{r}

enrichmentResult$results %>% arrange(CorrectedMFPvalue)

```
































































































































